Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-07 doc/slides/hong+eisner.TLT13.slides.tex
removed some slides. Moved some slides. Working on the ILP slides

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{7}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{5}{}
      \depedge[edge above, thick, hide label]{5}{4}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label, edge unit distance = 1.8ex]{7}{2}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of \textit{with} as well as the subject of \textit{fell}.}
  \end{figure}
}

\subsection{Conjunction}
\frame{\frametitle{Conjunction}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jack \& and \& Jill \& went \& up \& the \& hill \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 1.5ex]{4}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{4}{2}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge above, thick, hide label]{5}{7}{}
      \depedge[edge above, thick, hide label]{7}{6}{}

@@

\section{Non Projectivity}
\frame{\frametitle{We do not address: Non-Projectivity}
\begin{itemize}
  \item Projectivity assumptions allow us to have efficient parsing algorithms that utilize dynamic programming
  \item English is mostly projective
\end{itemize}

\NoteJH{Should I mention non-projectivity? This slide is mostly here because of a reviewer comment.}
}

\frame{\frametitle{We do not address: Non-Projectivity}
\begin{itemize}
  \item Projectivity assumptions allow us to have efficient parsing algorithms that utilize dynamic programming
  \item English is mostly projective
\end{itemize}

\begin{figure}
  \includegraphics[width=0.7\linewidth]{multiheaded}
  \caption*{But not always}
  \NoteJH{image taken from Chris Dyer's slide: http://demo.clab.cs.cmu.edu/fa2014-11711/images/0/0e/Depparsing.pdf}
  \NoteJH{I should also ask Chris for permission to use this}
\end{figure}

@@

\section{ILP Model}
\frame{\frametitle{Integer Linear Programming Model: Variables}

For each sentence, for each edge $i,j$ where $i < j$, we introduce variables $x_{ij}$ and $x_{ji}$.

\NoteJH{TODO: Incomplete slide. Need to describe things like depth of the variable, label}
}

\frame{\frametitle{Integer Linear Programming Model: Encoded Constraints}

\begin{itemize}
  \item Connectedness
  \item Acyclicity
  \item Consistency of Directionalized Links
\end{itemize}

@@

@@

  \item[] Acyclic
    \begin{align}
      (\forall_u)\; d_v + (1 + n_v) \cdot (1 - x_{uv}) & \geq 1+d_u
    \end{align}
\end{itemize}

@@

    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
    \item[]
  \end{itemize}
}

@@

    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
    \item[] The link labels mostly have a consistent direction.
  \end{itemize}
}

>>>>

\subsection{Relativization}
\frame{\frametitle{Relativization}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        The \& boy \& that \& Jill \& skipped \& with \& fell \& down \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 2ex]{7}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{3}{5}{}
      \depedge[edge above, thick, hide label]{5}{4}{}
      \depedge[edge above, thick, hide label]{5}{6}{}
      \depedge[edge above, thick, hide label, edge unit distance = 1.8ex]{7}{2}{}
      \depedge[edge above, thick, hide label]{7}{8}{}
      \depedge[edge below, ultra thick, hide label, edge style = {purple}, edge unit distance = 1.5ex]{6}{2}{}
    \end{dependency}
    \caption*{The boy is the object of \textit{with} as well as the subject of \textit{fell}.}
  \end{figure}
}

\subsection{Conjunction}
\frame{\frametitle{Conjunction}
  \begin{figure}
    \begin{dependency}
      \begin{deptext}
        Jack \& and \& Jill \& went \& up \& the \& hill \\
      \end{deptext}
      \deproot[edge above, thick, hide label, edge unit distance = 2ex]{4}{}
      \depedge[edge above, thick, hide label]{2}{1}{}
      \depedge[edge above, thick, hide label]{2}{3}{}
      \depedge[edge above, thick, hide label]{4}{2}{}
      \depedge[edge above, thick, hide label]{4}{5}{}
      \depedge[edge above, thick, hide label]{5}{7}{}
      \depedge[edge above, thick, hide label]{7}{6}{}

@@

%\section{Non Projectivity}
%\frame{\frametitle{We do not address: Non-Projectivity}
%\begin{itemize}
%  \item Projectivity assumptions allow us to have efficient parsing algorithms that utilize dynamic programming
%  \item English is mostly projective
%\end{itemize}

%\NoteJH{Should I mention non-projectivity? This slide is mostly here because of a reviewer comment.}
%}

%\frame{\frametitle{We do not address: Non-Projectivity}
%\begin{itemize}
%  \item Projectivity assumptions allow us to have efficient parsing algorithms that utilize dynamic programming
%  \item English is mostly projective
%\end{itemize}

%\begin{figure}
%  \includegraphics[width=0.7\linewidth]{multiheaded}
%  \caption*{But not always}
%  \NoteJH{image taken from Chris Dyer's slide: http://demo.clab.cs.cmu.edu/fa2014-11711/images/0/0e/Depparsing.pdf}
%  \NoteJH{I should also ask Chris for permission to use this}
%\end{figure}

@@

\section{ILP Model}

\frame{\frametitle{Integer Linear Programming Model}

Encoded Constraints:
\begin{itemize}
  \item Connectedness
  \item Acyclicity
  \item Consistency of Directionalized Links
\end{itemize}

@@

\frame{\frametitle{Integer Linear Programming Model}

For each sentence, for each edge $i,j$, where $i < j$

\begin{figure}
  \begin{dependency}[edge style={-}]
    \begin{deptext}
      . \& . \& . \& $i$ \& . \& . \& . \& $j$ \& . \& . \& . \\
    \end{deptext}
    \depedge[edge above, thick, edge unit distance = 1.1ex]{4}{8}{L}
  \end{dependency}
\end{figure}

Variables:

\begin{itemize}
\item $x_{ij}, x_{ji} \in \mathbb{Z} \geq 0$ representing the orientation of each link

$x_{ij} + x_{ji} = 1$

%\item $x_{ij} + x_{ji} = 1$ (A link can only be oriented left or right)

\end{itemize}

%\NoteJH{TODO: Incomplete slide. Need to describe things like depth of the variable, label}
}

@@

  \item[] Acyclicity
    \begin{itemize}
      \item a
    \end{itemize}

    \begin{align}
      (\forall_u)\; d_v + (1 + n_v) \cdot (1 - x_{uv}) & \geq 1+d_u
    \end{align}
\end{itemize}

@@

    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
  \end{itemize}

  \begin{itemize}
  \item[]
  \end{itemize}
}

@@

    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
  \end{itemize}

  \begin{itemize}
  \item[] The link labels mostly have a consistent direction.
  \end{itemize}
}
